---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# splattr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/splattr)](https://CRAN.R-project.org/package=splattr)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/ijlyttle/splattr.svg?branch=master)](https://travis-ci.org/ijlyttle/splattr)
<!-- badges: end -->

The goal of splattr is to provide some HTML-based tools for viewing and evaluating color-palettes. It is strongly inspired by the approach that Mike Bostock takes to show d3 color-palettes in [Observable](https://observablehq.com/@d3/working-with-color).

## Installation

You can install the delevopment version of codefolder from [GitHub](https://github.com/ijlyttle/splattr) with:

``` r
# install.packages("devtools")
devtools::install_github("ijlyttle/splattr")
```

## Examples

These examples are not run in the README because I am not able to get `swatch()` and `ramp()` to print outside of an HTML context.

You can see them in action in ihe [get-started article](https://ijlyttle.github.io/splattr/articles/splattr.html).

```{r, out.height="auto", eval=FALSE}
library("splattr")

colors <- colorspace::terrain_hcl(10)

swatch(colors)

ramp(colors)
```

## Contributing 

Please note that the 'splattr' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
